\class : Week \psetnum

### 2022-11-07 541_ism/week6/solutions.tex
remove mhchems
the spectra are done, and my braincells are gone

\documentclass[12pt, letterpaper, twoside]{article}
\usepackage{nopageno,epsfig, amsmath, amssymb}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{mhchem}
\usepackage{array}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}
\usepackage{empheq}
\usepackage{wrapfig}

@@

\newcommand{\psetnum}{5}
\newcommand{\class}{ASTR 541 - Interstellar Medium}

@@

\question{\textbf{1. Spectroscopy}}
\answer{
    z=0.1657
    583.826, 459.247

    ratio = 1.27, low density?

    OII=14772.4, 2715.04 (Hbeta)

    NII=130.103, Halpha=9469.3

    Second file
    z=0.22833

    SII: 18.8138, 14.4956: ratio=1.298, low density

    OIII: 16.6357, Hbeta=36.7896

    NII=83.1522, Halpha=150.604
}

>>>>

\documentclass[12pt, letterpaper, twoside]{article}
\usepackage{nopageno,epsfig, amsmath, amssymb}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}
\usepackage{empheq}
\usepackage{wrapfig}

@@

\newcommand{\psetnum}{6}
\newcommand{\class}{ASTR 541 - Interstellar Medium}

@@

\question{\textbf{1. Spectroscopy}}
\answer{
    I'm going to summarise my results in a single table to make it a bit easier to parse.
    \begin{center}
        \boxed{
        \begin{tabular}{l|c|c|c|c|c|c}
            Galaxy & Redshift & SII Ratio & O3HB & N2 & O3N2 & Oxygen Abundance \\
            \hline
            J0929+4644\_172\_157 & 0.017 & 1.27 & 5.45 & 0.05 & 2.06 & 8.17 \\
            J0943+0531\_106\_34 & 0.228 & 1.30 & 0.43 & 0.55 & -0.11 & 8.77
        \end{tabular}}
    \end{center}
    \textbf{Density regimes:} Both of these galaxies are in a low density regime since the SII ratios are both close to 1.44 (which we calculated in the last homework).

    \noindent \textbf{Spectrum Noise:} The second galaxy is noisier because it is at a higher redshift and therefore all fluxes are lower.

    \noindent \textbf{Galaxy Masses:} The second galaxy has a higher oxygen abundance. Therefore I think this means that \textbf{the second galaxy must be more massive}. The reason for this is that massive stars enrich the gas and increase the oxygen abundance. So a higher stellar mass would result in a larger oxygen abundance.
}
